### 2013-09-17 thesis-proposal/timeline.tex
Updated beginning of proposal

\section{Research Plan}

\subsection{Spring 2013}
I will complete the work on Ace and active type theory and submit it for publication.

\subsection{Summer 2013}
I will complete the work on active code prediction and submit it for publication.

\subsection{Fall 2013}
I will finalize all work and write the final dissertation.

>>>>

% !TEX root = omar-thesis-proposal.tex
\section{Timeline}

\subsection{Fall 2013}
I will complete the work on Ace (ESOP - Oct.) and active type theory (PLDI - Nov.) and Wyvern (ECOOP - Dec.) and submit each for publication.

Ace:
- Finish implementation
- Finish OpenCL implementation
- Finish C implementation
- Implement global arrays, functional data parallelism, objects

Theory:
- Prove metatheory (mechanized?)
- Figure out composition theorem
- Figure out how it would look in Coq

Wyvern:
- Figure out grammar and type system formalism
- See implementation through
- Declarative stuff
- Write it up

Graphite:
- Figure out safety stuff

\subsection{Spring 2014}
I will finalize all work and write the final dissertation.

%\subsection{Summer 2014}
